\pkg{cv}: An \proglang{R} Package for Cross-Validation of Regression Models

### 2024-01-14 scratch/notes_john/JSS-article/JSS-article-reduced-2.Rmd
updates NEWS file; add Georges's orcid

---
documentclass: jss
author:
  - name: John Fox
    orcid: 0000-0002-1196-8012
    affiliation: 'McMaster University'
    address: |
      | Hamilton, Ontario, Canada
    email: \email{jfox@mcmaster.ca}
    url: https://www.john-fox.ca/
  - name: Georges Monette
    orcid: 0000-0000-0000-0000
    affiliation: 'York University'
    # To add another line, use \AND at the end of the previous one as above
    address: |
      | Toronto, Ontario, Canada
title:
  formatted: "\\pkg{cv}: An \\proglang{R} Package for Cross-Validation of Regression Models"
  # If you use tex in the formatted title, also supply version without
  plain:     "cv: An R Package for Cross-Validation of Regression Models"
  # For running headers, if needed
  short:     "\\pkg{cv}: Cross-Validation of Regression Models"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [cross-validation, regression analysis, model selection, "\\proglang{R}"]
  plain:     [cross-validation, regression analysis, model selection, R]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
    extra_dependencies: "subfig"
bibliography: ["cv.bib"]
---

@@

## Example: Contrived hierarchical data

>>>>

---
documentclass: jss
author:
  - name: John Fox
    orcid: 0000-0002-1196-8012
    affiliation: 'McMaster University'
    address: |
      | Hamilton, Ontario, Canada
    email: \email{jfox@mcmaster.ca}
    url: https://www.john-fox.ca/
  - name: Georges Monette
    orcid: 0000-0003-0076-5532
    affiliation: 'York University'
    # To add another line, use \AND at the end of the previous one as above
    address: |
      | Toronto, Ontario, Canada
title:
  formatted: "\\pkg{cv}: An \\proglang{R} Package for Cross-Validation of Regression Models"
  # If you use tex in the formatted title, also supply version without
  plain:     "cv: An R Package for Cross-Validation of Regression Models"
  # For running headers, if needed
  short:     "\\pkg{cv}: Cross-Validation of Regression Models"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [cross-validation, regression analysis, model selection, "\\proglang{R}"]
  plain:     [cross-validation, regression analysis, model selection, R]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
    extra_dependencies: "subfig"
bibliography: ["cv.bib"]
---

@@

## Example: CV of clusters versus individuals using contrived data

### 2024-01-14 scratch/notes_john/JSS-article/JSS-article-reduced-2.tex
updates NEWS file; add Georges's orcid

\author{
John Fox~\orcidlink{0000-0002-1196-8012}\\McMaster
University \And Georges Monette~\orcidlink{0000-0000-0000-0000}\\York
University
}
\title{\pkg{cv}: An \proglang{R} Package for Cross-Validation of
Regression Models}

@@

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 352413
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.42674
bias-adjusted cross-validation criterion = 19.40347
95% CI for bias-adjusted CV criterion = (15.89518, 22.91177)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\hypertarget{example-contrived-hierarchical-data}{%
\subsection{Example: Contrived hierarchical
data}\label{example-contrived-hierarchical-data}}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat){
  if (!all(y %in% c(0, 1))) stop("response values not all 0 or 1")
  if (any(yhat < 0) || any(yhat > 1)) stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x128c4cd38>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}

>>>>

\author{
John Fox~\orcidlink{0000-0002-1196-8012}\\McMaster
University \And Georges Monette~\orcidlink{0000-0003-0076-5532}\\York
University
}
\title{\pkg{cv}: An \proglang{R} Package for Cross-Validation of
Regression Models}

@@

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 801552
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.32751
bias-adjusted cross-validation criterion = 19.30935
95% CI for bias-adjusted CV criterion = (15.83674, 22.78196)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\hypertarget{example-cv-of-clusters-versus-individuals-using-contrived-data}{%
\subsection{Example: CV of clusters versus individuals using contrived
data}\label{example-cv-of-clusters-versus-individuals-using-contrived-data}}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat){
  if (!all(y %in% c(0, 1))) stop("response values not all 0 or 1")
  if (any(yhat < 0) || any(yhat > 1)) stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x123a02cc0>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}
